Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-01-13 tex/sections/intro.tex
Improve readability of the first part of "intro"
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

At the time of writing of this document,
the total mining reward for a Bitcoin block is around \$150,000. If we assume, in decision theoretic terminology,
that the mining reward accurately defines the utility function of a Bitcoin miner, one could hire all hashing power
of the Bitcoin network for one hour by
spending only \$750,000. The situation is not much different for PoS blockchains, as long as the total
stake of the validator set is a relatively small value. By
stake, we mean a real number measuring the total interest of a user in the system, we are not referring, in
particular, to some locked amount of a user's money that is known as stake in some PoS protocols.
This problem is more severe in blockchains that use randomly selected small sets of validators. These small sets
usually have low total stake and could be easily bribed and corrupted. Selecting these random sets
by hidden random procedures would not help, since the validator himself knows he has been selected, before casting
his vote.

@@

However, for effective participation in the consensus protocol, a validator needs to be able to detect
illegal transactions. Detecting illegal transactions can be done by accessing the ledger
state and executing transactions according to the protocol rules. The
ledger state, even for small blockchains, could be several
hundreds of gigabytes, and executing transactions could easily become costly when a blockchain is acting as a
smart contract platform. This computational and storage overhead, in practice, could prevent most of
ordinary users from any type of participation in the process of securing a blockchain.

Although a fully decentralized blockchain based on the participation of every user looks appealing, it is not as perfect
as it might seem. The consensus protocol of a blockchain relies on a network of computers, not humans. Ordinary users
use simple and similar computer systems. That means, they all have similar vulnerabilities and weaknesses which could be
used by an adversary to catastrophically attack the consensus protocol. For instance, if a malware, probably using a
common zero-day
vulnerability, has the ability to infect a large portion of normal personal computers, an adversary can use it to
take control of the majority of participants in the consensus protocol and compromise the security of the
blockchain.

>>>>

At the time of writing of this document,
the total mining reward for a Bitcoin block is around \$150,000, and the Bitcoin network approximately produces 5 blocks
per hour. If we assume, in decision theoretic terminology, that the mining reward solely defines the utility
function\footnote{In decision theory, the utility function measures the preference, worth or value of different
alternatives for a decision maker.} of a Bitcoin miner, one should be able to hire all hashing power
of the Bitcoin network for one hour by
spending only \$750,000. The situation is not much different for PoS blockchains, as long as the total
stake\footnote{Here by stake, we mean a real number measuring the total interest of a user in the system, and we are
not referring, in particular, to some locked amount of a user's money that is known as stake in some PoS protocols.}
of the validator set is a relatively small value.
This problem is even more severe in blockchains that use randomly selected small sets of validators. These small sets
usually have low total stake and could be easily bribed and corrupted. Selecting these random sets
by hidden random procedures would not help, since the validator himself knows he has been selected before casting
his vote.

@@

However, for effective participation in the consensus protocol, a validator needs to be able to detect
illegal transactions. Detecting illegal transactions can be done by accessing the ledger
state and executing transactions according to the protocol rules. The
ledger state, even for small blockchains, could be several
hundreds of gigabytes, and executing transactions could easily become costly when a blockchain is acting as a
smart contract platform. This computational and storage overhead, in practice, could prevent most of
ordinary users from any type of participation in the consensus protocol of a blockchain.

A fully decentralized blockchain based on the participation of every user looks appealing, though it is not as perfect
as it might seem. The consensus protocol of a blockchain relies on a network of computers, not humans. Ordinary users
use simple and similar computer systems. That means, they all have similar vulnerabilities and weaknesses which could be
used by an adversary to catastrophically attack the consensus protocol. For instance, if a malware, probably using a
common zero-day
vulnerability, has the ability to infect a large portion of normal personal computers, an adversary can use it to
take control of the majority of participants in the consensus protocol and compromise the security of the
blockchain.
